Manuscript_Github_Pchabaudi_calculateTPM

### 2022-07-22 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_calculateTPM.Rmd
Use the times of the life cycle stages for the pseudogene TPM graph

chab_tpm_melt.df <- reshape2::melt(chab_tpm.df,
                                   variable.name = 'sample',
                                   value.name = 'tpm') %>% 
  mutate(time = str_extract(sample, 
                            pattern = '([[:digit:]]{2}h_.+|sch.culture)(?=_[[:digit:]])'),
         transmission = str_extract(sample,
                                    pattern = 'rMT|SBP'))

(plot <- ggplot(data = filter(chab_tpm_melt.df, 
                     Geneid %in% 'PCHAS_0420800'), 
       aes(x = time, 
           y = log1p(tpm),
           fill = transmission)) +
  stat_summary(fun = median, fun.min = median, fun.max = median,
               geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
  geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = cbPalette) +
  theme_classic() +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5)))

>>>>

chab_tpm_melt.df <- reshape2::melt(chab_tpm.df,
                                   variable.name = 'sample',
                                   value.name = 'tpm') %>% 
  mutate(time = str_extract(sample, 
                            pattern = '([[:digit:]]{2}h|sch.culture)'),
         transmission = str_extract(sample,
                                    pattern = 'rMT|SBP'))

(plot <- ggplot(data = filter(chab_tpm_melt.df, 
                     Geneid %in% 'PCHAS_0420800'), 
       aes(x = time, 
           y = tpm,
           fill = transmission)) +
  stat_summary(fun = median, fun.min = median, fun.max = median,
               geom = "bar", width = 0.75, size = 0.25, position = 'dodge') +
  geom_point(stat = 'identity', position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = cbPalette) +
  theme_classic() +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5)))
